О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
One more link to extrenal paper
Add note about symmetry to the construction

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ (and every characteristic $q$~--- see~\cite{kurz2005characteristic} for details)
there exists a facher set $M\in\mathfrak{M}(2,n)$ (with the desired characteristic~\cite[Theorem 5]{our-vmmsh-2018}).

@@

Summing up Construction~\ref{con:planar_set_with_minimeter_1} above and~\cite[lemma 3 and proposition 6]{our-vmmsh-2018},
we obtain the following

@@

	And vice versa, if $M$ is a planar integral point set of $n$ points
	such that for some $M_1,M_2 \in M$ equality $|M_1 - M_2|=1$ holds,
	then $M$ consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line and one point out of the line.
	Moreover, if $n > 3$, then the distance 1 occurs in $M$ only once.
\end{theorem}

>>>>

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ (and every characteristic $q$~--- see~\cite{kurz2005characteristic} for details)
there exists a facher set $M\in\mathfrak{M}(2,n)$ (with the desired characteristic~\cite[Theorem 5]{our-vmmsh-2018}).
In~\cite{antonov2008maximal}, the facher sets of characteristic 1 are called \textit{semi-crabs} and investigated.

@@

Summing up Construction~\ref{con:planar_set_with_minimeter_1} above with~\cite[lemma 3 and proposition 6]{our-vmmsh-2018}
and~\cite[Section 6]{antonov2008maximal},
we obtain the following

@@

	And vice versa, if $M$ is a planar integral point set of $n$ points
	such that for some $M_1,M_2 \in M$ equality $|M_1 - M_2|=1$ holds,
	then $M$ consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line,
	and one point out of the line, on the bisector of line segment $M_1 M_2$.
	There is only one maximal integral point set $M' \supseteq M$,
	and the bisector is the axis of symmetry for $M'$.
	Moreover, if $n > 3$, then the distance 1 occurs in $M$ (and $M'$) only once.
\end{theorem}
